Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2015-10-07 paper.tex
timestep doesn't introduce quantized shutdown but amplifies it
Expand example to list form

One difference between the fleet and individual facility modeling is the
\emph{quantized shutdown effect}.  If a fleet-based reactor modeling 3-batch
cores is short one half batch of fuel, it will produce $\frac{2.5}{3}\cdot P_r$
of power for that time step where $P_r$ is the power capacity of a single
reactor of the fleet (\emph{e.g.}~1000~MWe).  If an individually modeled reactor is
short a half batch of fuel, then it will produce no power ($0 \cdot P_r$) that
time step.  Time step duration can also have this effect.  For both fleet and
individual reactor modeling, power goes offline in full time step increments.
For example, if a 3-batch fleet based reactor is short $\frac{1}{2}$ batch of
fuel with a 3 month time step, then it will produce $\frac{2.5}{3} \cdot 3
\text{mo} \cdot P_r$ of energy.  In contrast, a monthly time step might allow
the same reactor to produce $[\frac{2.5}{3} \cdot 1 \text{mo} + 1 \cdot 2
\text{mo}] \cdot P_r $ of energy if the fuel shortage actually ended after only
1 month.  Quantifying this effect directly is difficult.  One way of observing
it is to compare fleet reactor scenarios that have different time step
durations (i.e. cases MF and QF).  Because the fleet reactors have perfect fuel
sharing (described below) and no noise from refueling outages, differences observed will
likely be due to quantized shutdown.

>>>>

One difference between the fleet and individual facility modeling is the
\emph{quantized shutdown effect}.  If a fleet-based reactor modeling 3-batch
cores is short one half batch of fuel, it will produce $\frac{2.5}{3}\cdot P_r$
of power for that time step where $P_r$ is the power capacity of a single
reactor of the fleet (\emph{e.g.}~1000~MWe).  If an individually modeled reactor is
short a half batch of fuel, then it will produce no power ($0 \cdot P_r$) that
time step.  Time step duration can amplify this effect.  For both fleet and
individual reactor modeling, power goes offline in full time step increments.
Consider an example of a 3-batch reactor with a fuel shortage of $\frac{1}{2}$ batch of
fuel that would be resolve in 1 month.  Depending on the modeling choice, each reactor
would produce the following amounts of energy over a 3 month period:

\begin{itemize}
  \item case \emph{QF}: $\frac{2.5}{3} \cdot 3 \text{mo} \cdot P_r = 2.5P_r$
  \item case \emph{MF}: $[\frac{2.5}{3} \cdot 1 \text{mo} + 1 \cdot 2
    \text{mo}] \cdot P_r = 2.83P_r$
  \item case \emph{QI}: $0 \cdot 3 \text{mo} \cdot P_r = 0$
  \item case \emph{MI}: $[0\cdot 1 \text{mo} + 1 \cdot 2\text{mo}] \cdot P_r = 2 P_r$
\end{itemize}

Quantifying this effect directly is difficult.  One way of observing
it is to compare fleet reactor scenarios that have different time step
durations (i.e. cases MF and QF).  Because the fleet reactors have perfect fuel
sharing (described below) and no noise from refueling outages, differences observed will
likely be due to quantized shutdown.
